The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete v0.3

### 2014-01-02 main/s_level_2.tex
fixes to proof ideas

\begin{definition}
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,w)$ consists of a set of vertices $V$ with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set of undirected edges $E\subseteq V\times V$ with \emph{weight} $w\colon E\to N$.

A \emph{configuration} of an \textsc{ncg} is a function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
for every edge $e$ connecting vertices $v$ and $w$, $\gamma(e)\in\{v,w\}$, and
	\item
for every vertex $v$, the sum of its inflow weights $\sum\{w(e)\mid \gamma(e)=v\}$ is equal to or greater than its inflow constraint $c(v)$.
\end{itemize}

@@

The interpretation of the graph $G$ is the sequent
\[
	\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
\]
where $m=k\times(|w|-|c|)\times(3n+4)$.

@@

By the above, a proof net $\links$ for $\itn G$ gives a partial function $\coitn\links\colon E\rightharpoonup V$.

\begin{lemma}
If $\links\sim\links'$ is the re-attachment of one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
\end{lemma}

\begin{proof}
TO DO
\end{proof}

In a proof net for the interpretation of a graph $\itn G$, call an edge-gadget $\itn e$ with $e=(u,w)$ \emph{appropriate} for a vertex-gadget $\itn v$ if $v\in\{u,w\}$, and \emph{inappropriate} otherwise.

\begin{lemma}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the

\end{lemma}

>>>>

\begin{definition}
A \emph{non-deterministic constraint graph} (\textsc{ncg}) $G=(V,E,c,v,w)$ consists of a set $V$ of vertices with \emph{minimum inflow constraint} $c\colon V\to\mathbb N$, and a set $E$ of at most one undirected edge $e$ per vertex-pair $v(e)=\{v_1,v_2\}$, with \emph{weight} $w\colon E\to N$.

A \emph{configuration} of an \textsc{ncg} is a function $\gamma\colon E\to V$ such that
\begin{itemize}
	\item
$\gamma(e)\in v(e)$ for every edge $e$, and
	\item
for every vertex $v$, the sum of its inflow weights $\sum\{w(e)\mid \gamma(e)=v\}$ is equal to or greater than its inflow constraint $c(v)$.
\end{itemize}

@@

The interpretation of the graph $G$ is the sequent
\[
	%\itn G = \bigotimes_{1\leq i\leq n}\itn{v_i}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
	\itn G = \itn{v_1}\tn\dotso\tn\itn{v_n}, \itn{e_1},\dotsc,\itn{e_k}, \bot^m
\]
where $m=k\times(|w|-|c|)\times(3n+4)$.

@@

%\begin{lemma}
%If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then $\coitn\links$ and $\coitn{\links'}$ differ on the value of at most one edge.
%\end{lemma}

% THIS IS FALSE : OTHER EDGES MAY BE CONNECTED *VIA* THE ONE THAT IS MOVED

By the above, a proof net for $\itn G$ gives a partial function from edges to vertices.

\begin{definition}
	For a proof net $\links$ for the interpretation of a graph $\itn G$, let $\coitn\links\colon E\rightharpoonup V$ be the partial function where $\coitn\links(e)$ is $v$ if $\itn e$ belongs to the empire of $\itn v$, and undefined otherwise.
\end{definition}

In an \textsc{ncg} $G$, an edge $e$ will be called \emph{appropriate} for a vertex $v$ if $v\in v(e)$, and \emph{inappropriate} otherwise.
%
This notion is extended to edge-gadgets $\itn e$ and vertex-gadgets $\itn v$ in $\int G$.

\begin{lemma}
If the permutation $\links\sim\links'$ consists of the re-attachment of exactly one jump, then from $\coitn\links$ to $\coitn{\links'}$ at most one edge is taken from one appropriate vertex to another.
\end{lemma}

\begin{proof}[Proof sketch]
At most, a link can re-connect from vertex-gadget $v$ to vertex-gadget $w$, moving a number of chained edge-gadgets from $v$ to $w$.
%
But at most one edge is appropriate for both $v$ and $w$.
\end{proof}

\begin{lemma}
In a proof net for $\itn G$, for each vertex $v$, the weights of the appropriate edge-gadgets in the empire of $\itn v$ are equal to or greater than the constraint of $v$.
\end{lemma}
